---
output: github_document
bibliography: bib.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Reproduce the Results of @gerard2019priors

## Introduction

This repository contains the code and instructions needed to reproduce all of
the results from @gerard2019priors.

If you find a bug, please create an
[issue](https://github.com/dcgerard/reproduce_prior_sims/issues).

## Instructions
    
1. Install the appropriate R packages
    ```{r, eval = FALSE}
    install.packages(c("updog",
                       "tidyverse", 
                       "vcfR",
                       "ggthemes",
                       "doSNOW",
                       "knitr",
                       "CVXR"))
    ```
    
2. Download the data from @uitdewilligen2013next.

    Place the file "journal.pone.0062355.s007.GZ" in the "data" folder.
    
    You can obtain this file from <https://doi.org/10.1371/journal.pone.0062355.s007>.
    
    This step is optional since running `make` will attempt to download all of
    the required data using `wget`.
    
3. Download the data from @shirasawa2017high.

    Place the file "KDRIsweetpotatoXushu18S1LG2017.vcf.gz" in the "data" folder.
    
    You can obtain this file from
    <ftp://ftp.kazusa.or.jp/pub/sweetpotato/GeneticMap/KDRIsweetpotatoXushu18S1LG2017.vcf.gz>.
    
    This step is optional since running `make` will attempt to download all of
    the required data using `wget`. 

4. Adjust the Makefile. Change the `nc` and `rexec` variables in the Makefile
   according to your local computing environment. For example, you would need
   to decrease `nc` if you have fewer than 12 CPU cores. You can check the 
   number of CPU cores you have by typing the following in R:
   
    ```{r, eval=FALSE}
    parallel::detectCores()
    ```

5. Run `make`.
    - To reproduce all of the results in the paper, simply run in the terminal:
        ```{bash, eval=FALSE}
        make
        ```
    - To reproduce just the example bad behavior under the general or uniform priors, run in the terminal:
        ```{bash, eval=FALSE}
        make example
        ```
    - To reproduce just the simulation results, run in the terminal:
        ```{bash, eval=FALSE}
        make sims
        ```
    - To reproduce just the real data results, run in the terminal:
        ```{bash, eval=FALSE}
        make realdata
        ```
    - To reproduce just the computational comparisons, run in the terminal:
        ```{bash, eval=FALSE}
        make f1comp 
        make unicomp
        ```
    - To reproduce the figure demonstrating the flexibility of the class
      of proportional normal distributions, run in the terminal:
        ```{bash, eval=FALSE}
        make normal
        ```
    
6. Get coffee. Running `make sims` should take a few hours. You should get 
   some coffee! Here is a list of some of my favorite places:

    - Washington, DC
        - [Colony Club](https://www.yelp.com/biz/colony-club-washington)
        - [Grace Street Coffee](https://www.yelp.com/biz/grace-street-coffee-georgetown)
        - [Shop Made in DC](https://www.yelp.com/biz/shop-made-in-dc-washington)
    - Chicago
        - [Sawada Coffee](https://www.yelp.com/biz/sawada-coffee-chicago)
        - [Plein Air Cafe](https://www.yelp.com/biz/plein-air-cafe-and-eatery-chicago-2)
    - Seattle
        - [Bauhaus Ballard](https://www.yelp.com/biz/bauhaus-ballard-seattle)
        - [Cafe Solstice](https://www.yelp.com/biz/cafe-solstice-seattle)
    - Columbus
        - [Yeah, Me Too](https://www.yelp.com/biz/yeah-me-too-columbus)
        - [Stauf's Coffee Roasters](https://www.yelp.com/biz/staufs-coffee-roasters-columbus-2)

## Package Versions

If you are having trouble reproducing these results, check your package 
versions. These are the ones that I used:

```{r, echo = FALSE, message=FALSE, warning=FALSE, results='hide'}
package_vec <- c("updog",
                 "tidyverse",
                 "vcfR",
                 "ggthemes",
                 "doSNOW",
                 "knitr",
                 "CVXR")
lapply(package_vec, library, character.only = TRUE)
```

```{r}
sessionInfo()
```

Note that I've also only tried this on Ubuntu.

## References
    

